---
title: "Climate"
author: "Faith Igomodu"
date: "August 29, 2024"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Visiualizing Climate Change Data With ggplot2

  Climate change is here and observing its trends using historical tempeature data paints a daunting image of a future where live as we know it is drastically different. To explore these trends through visualization, obtained temperature data and studied it using ggplot2.
  Average mean temperature, minimum temperature and maxiumum temperature   from the National Center for Environmental Information (NCEI) for Richmond, Virgina (station number USW00013740) between 1983-2019 was obtained. 
  
## Install and load libraries 

Expecting the time series dataset may contained missing values, Times Series Missing Vlaue imputation in R (imputeTS) package is used to fill in any missing data. The imputeTS pacakge uses state-of-the-art imputation algorithm to replace missing values. 

```{r}
#install.packages("imputeTS", quiet = T)
```


```{r}
library(ggplot2)
library(tidyverse)
library(readr)
library(imputeTS)
```

## Read dataset 

Read, clean and sumarize the dataset. 

```{r}
df <-read_csv("3785897.csv")
head(df)
```


```{r}
summary(df)
```



















